---
title: "Aides Drug"
author: "Adriana Pimentel"
date: "10/7/2021"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
triUmp <-read.csv(file="triUmpsal.csv",header=TRUE)
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

A new  preventative aides drug (triUmpsal) is under test in clinical trials. Consider only the females, does this drug seem effective?  Hint - use dplyr to obtain that subpopulation with the filter command.

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->

First we have to condense the data frame so that only women are in it and analyze it to see if the drugs are effective.  

```{r}
girls<-filter(triUmp,gender=="F")
```


# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

```{r}
dd2 <- girls %>% group_by(infected,treatment) %>% summarize(count=n()) %>% mutate(prcnt=count/sum(count))


# the group_by followed by summarize(count=n())

basicC <- ggplot(dd2,aes(x=infected,y=count,fill=treatment))
basicC + geom_bar(stat="identity",position="dodge")

#Now for percentage plot

basicCC <- ggplot(dd2,aes(x=infected,y=prcnt*100,fill=treatment)) 
basicCC + geom_bar(stat="identity", position = "dodge")
```
  
In the graph above we are shown that about 60% of the females with aids took the drug and the other 40% of the women with aids took the placebo. This means that the drug did not work because there is a higher percentage of females with aids that took the drug than the females that took the placebo.   

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
table1 <- xtabs(~infected + treatment, data=girls)
rowPerc(table1)
colPerc(table1)
```
    
The numerical results shows the exact percentage of females with aids that took the drug and the females with aids that took the placebo which was 58.82% and 41.18% respectively. Which proves that this drug does not work in preventing aids.    
  
## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```
  
The inferential results shows two low p-values which means that we reject the null hypothesis that there is no difference between those who take the drug and those who take the placebo, because there is a difference. As shown in the Fisher's Exact Test: it demonstrates an odds ratio of 1 and a half to 1 of being prone to aids if you take the drug. Which means the purpose of the drug did not work. More females that took the drug, got aids. So, the drug did not decrease the chances of getting aids, instead, it increased the chances of getting aids.   

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
  
In the beginning, we had to narrow down the data frame to females only. Then we pulled out the graphical results which showed a plot of how many females had aids and how many did not. The other plot showed the effectiveness of the drug. Which proved to be not effective. The numerical results was that about 60% of the females who took the drug had aids and about 40% of the females who took the placebo had aids. These results proved that the drug was not effective in decreasing the contraction of aids.  